### 2024-10-21 Scripts/Manuscript/manuscript.Rmd
final co-author feedback processing, before first submission.

---
title             : "An Empirical Assessment of Reliable and Valid Measurement as a Prerequisite for Informative Replications"
shorttitle        : "Measurement and Informative Replications"

@@

  - name          : "Bakker, M."
    affiliation   : "1"

  - name          : "Wicherts, J.M."
    affiliation   : "1"

  - name          : "Nuijten, M.B."
    affiliation   : "1"

@@

abstract: |
  Recent studies have shown that challenges in measurement practices may have contributed to the “replication crisis” in psychological science. 
  However, the nature and extent of the association between measurement and replicability remains unclear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability. 
  Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
  We additionally found that reliability and validity evidence was rarely reported. 
  Furthermore, logistic regression results indicated that "questionable measurement practices" (QMPs) in replication studies were associated with lower replicability (b = -5.60, p = .006), while study reliability was not (b = 8.21, p =. 106) . <!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.--> 
  These findings corroborate existing research that construct validity in published research is unknown, which may have negative consequences for replications. 
  We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
wordcount         : "166"

@@

For solid scientific progress in psychology, we need to be able to rely on previous findings - findings should be credible. Unfortunately, psychology seems to face several threats to the credibility of its findings. In this article, we investigate how the credibility of psychological findings may be related to problems in psychological measurement, and in turn, how those problems may affect subsequent replications.

## Credibility & Replicability

A prerequisite for a credible finding is that it is replicable [@vazire2022CredibilityReplicabilityImproving]. This means that the observed effect should be comparable across the original study and subsequent replications in new samples if the differences between them are believed to be of little relevance to the effect [@nosek2022replicability].

But replications often fail. In 2015, the Replication Project: Psychology [RPP\; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings . Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research. Furthermore, the estimates of the effect varied between different lab locations.

In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate. The factors that have been proposed include, questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another factor that has gained more traction recently is the impact of measurement-related challenges on replicability and credibility.

## Credibility & Measurement

Psychological constructs, such as affective state or intelligence, cannot be measured directly [@flake2017construct]. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].

The second issue relates to the concept of validity, specifically construct validity, or the overall extent to which a measure measures what it is supposed to measure [@borsboom2004concept]. Construct validity of test scores is often assessed by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct]. A researcher cannot claim to have found a credible psychological effect, if the measures do not relate to the psychological construct [@cook2002experimental].

@@

While reliable and valid measurement, as well as replicability are important elements that independently contribute to the overall credibility of a finding, there may also be a relation between them. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may be related to the chance of successfully replicating a psychological finding. This study aims to investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects.

Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts. Furthermore, as the Many Labs projects used preregistered and documented structured protocols, we therefore believe the measurement use in these projects represent a high standard within the field. Any issues in measurement here might suggest that other replications could face similar or greater challenges.

@@

While reliability is generally considered a measure specific feature, this is false. The reliability of a measure varies between samples [@cho2015cronbach; @pauly2018resampling]. Besides random variation due the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures are known to generally show lower reliability in more homogeneous samples as compared to heterogeneous samples [@pike1998reliability].

The resulting variations in the measurement scores could contribute to the discrepancy between effects in original and replication research, as well as within replications of the same original effect. After all it has long been known that noise in measurement suppresses observed effects and associations [@spearman1904proof]. @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research. The results showed that the variation due to measurement error was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations]. In summary, studies using unreliable measures are less replicable, even when the measurement is equally reliable between original and replication.

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. More specifically, @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@@

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers. In order to reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores. If the measure is not reconstructed exactly, constructs measured by original and replication may differ, which may lead to differences in effect size estimates irrespective of the credibility of the original effect.

@@

Our study investigated the relation of reliability and measurement reporting with replicability, using data and reports from the large scale Many Labs replication projects. First, this study expands on the research by @stanley2014expectations. Our goal was to see whether reliability was related to replication success in empirical replication data. Specifically, we investigated whether successfully replicated studies differed in reliability from non-replicated studies. @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to the relation between reliability and replication, this study also investigated the variation in reliability as observed across labs.

Furthermore, this research conceptually replicates the study by @flake2022construct on QMPs in replications and original research, now in the context of the Many Labs projects. We then expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.

@@

Measurement reliability varies across samples. Accounting for the differences between original and replication is crucial for evaluating replications. This includes variation in measurement reliability. Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a[^1]) and original psychological research (RQ1b). The Many Labs studies were intended as direct replications, which implies that any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability]. Therefore, we expected that there would be, no difference in reliability between replication research and original research (Hypothesis 1; H1).

@@

Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring]. We empirically investigated this in our sample by investigating whether reliability estimates differed between replicating labs (RQ2). For effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expect that there is no significant variation in the reliability estimates of replications of the same original study (H2) either.

In theory, there should be a positive relation between reliability and replicability. Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance. To empirically assess this, we investigated whether there is an association between replication study reliability and replication outcome (RQ3). We expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).

@@

This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct. To do so we evaluate how common QMPs are in replications of psychological research (RQ4a) and original psychological research (RQ4b).

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because othe Many :abs replications used structured protocols documenting the measurement.

QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts. The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct]. Therefore, we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).

A reduction in QMPs corresponds to greater transparency in reporting of measurement. In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).

@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research. @shaw2020measurement already found such a spill-over effect for validity. In line with this research we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6). We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

The data used for the analyses consisted of three main sources: replication datasets, replication protocols, and original study articles. The data came from the Many Labs replication projects. Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on item-based measures.

@@

The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was being replicated. Multiple psychological constructs could be measured per original study or replication. We used the replication protocols to identify these measures. Acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses were not included.

@@

We retrieved the data on the replication protocols, and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>) in the supplementary materials.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs that took part in a Many Labs study. For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below. When scores could not be clearly identified, any available codebooks, analysis scripts or study materials were used to identify the relevant scores.

To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

### Replication Protocols

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

The original study articles were identified using the citations for these articles in each replication protocol. All articles could be retrieved.

@@

Because data from the Many Labs replications were available for each lab location within each replication set, it was possible to calculate reliabilities for any item scale measure used for each lab location separately. This made it possible to assess the variation of reliabilities of the same measure across different contexts.

Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles. Cronbach's Alpha was calculated using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments. Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd).

@@

We extracted the reported reliability coefficient and type of index (Cronbach's Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present. Similarly, we coded the presence of any validity evidence, such as a factor analysis, that was presented alongside the measure.

The tests for Hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols. We included items based on @flake2022construct, and additional items to further assess transparent measurement reporting as laid out in @flake2020measurement. In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on @flake2020measurement. The QMP categories and example items can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

QMPs were all coded to be either true, false, or not applicable if not relevant for that measure (e.g. reporting results from a factor analysis for single item measures). For the analyses we calculated a ratio (both per QMP type and overall QMP) based on the number on the number of true responses divided by the number of responses coded to be applicable.

After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because they were considered too stringent in some of their criteria for what constituted a QMP. For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).

@@

We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many] to determine replication success based on the reported significance of the meta-analytic effect. An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.

@@

Every hypothesis test in this study was a two-sided test with an alpha of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low. Our hypotheses are about associations that have been proposed in the literature, but to the best of our knowledge have not yet been empirically tested on real data. In this exploratory context, false negatives were considered more detrimental than false positives.

@@

Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.

@@

### Hypothesis 6: Relation Between QMPs in Original and Replication Research.

>>>>

---
title             : "Assessing Reliable and Valid Measurement for Informative Replications in Psychology"
shorttitle        : "Measurement and Informative Replications"

@@

  - name          : "Bakker, Marjan"
    affiliation   : "1"

  - name          : "Wicherts, Jelte M."
    affiliation   : "1"

  - name          : "Nuijten, Michèle B."
    affiliation   : "1"

@@

abstract: |
  For a replication to be informative, measurement should be reliable and valid in both original and replication studies. 
  Recent studies have identified problems with measurement and measurement reporting in both original and replication studies, although the association between measurement and replicability remains unclear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and studied their association with replicability. 
  We found that not all measures were sufficiently reliable across contexts, and that only few measures were accompanied with reliability and validity evidence. 
  Furthermore, “questionable measurement practices” (QMPs) in replication studies were associated with lower replicability, while original study reliability was not. 
  These results corroborate existing findings that construct validity in published research is often unknown, which may complicate replication research. 
  We offer suggestions on improving measurement practices and argue that reported measurement information should inform the decision to replicate.

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replicability, credibility, psychology"
wordcount         : "159"

@@

Findings from psychological research should be credible to build and extend upon them. A credible finding must be replicable [@vazire2022CredibilityReplicabilityImproving], such that the observed effect is sufficiently comparable across the original study and subsequent replications in new samples and using nearly identical designs [@nosek2022replicability]. In this article, we investigate how the credibility of psychological findings relates to problems in psychological measurement and how measurement problems may affect subsequent replications.

Unfortunately, the Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects that sought to replicate earlier and seminal findings [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] typically yielded smaller effects in replications compared to original studies, with Many-Labs projects featuring different locations and samples. In response to this string of failed replications, there was widespread alarm regarding the credibility and robustness of findings in psychological science [@hughes2018psychology; @giner2019crisis], and efforts to explain the low replication rate. The factors that have been proposed include questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], and biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science]. Another important factor is the impact of measurement-related challenges on replicability and credibility.

## Credibility & Measurement
Psychological constructs, such as affective states or intelligence, cannot be measured directly. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

Reliability estimates provide an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].

Moreover, researchers cannot claim to have found a credible psychological effect if the measures do not relate to the psychological constructs [@cook2002experimental]. Validity indicates the extent to which a measure measures what it is supposed to measure [@borsboom2004concept] and can be studied by comparing the test scores’ empirical associations to the theoretical associations of the constructs [@cronbach1955construct].

@@

Replicability and reliable and valid measurement are essential elements of the credibility of a finding, and are related to each other. Indeed, recent studies have illustrated that both the reliability of the measure [@stanley2014expectations] and the reporting of information relevant to demonstrating the validity of the measurement [@shaw2020measurement; @flake2017construct; @flake2020measurement] may predict the replicability of psychological findings.

In this study, we investigate the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects. Because the Many Labs projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] are large-scale collaborations in which multiple lab locations directly replicated the same set of studies, their data allows us to study the variability in their measures across different contexts. Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement used in these projects to represent a high standard within the field. Any issues in measurement here might suggest that other replications could face similar or greater challenges.

@@

Notwithstanding the common yet mistaken belief that reliability is a measure-specific feature, the reliability of a measure typically varies between samples differing in latent trait variance and/or the latent measurement model [@cho2015cronbach; @pauly2018resampling]. Besides random variation due to the sampling error, the variations can also reflect true variation in reliability, also known as reliability heterogeneity [@vacha-haase1998ReliabilityGeneralizationExploring]. For instance, measures will normally show lower reliability in more homogeneous samples than heterogeneous samples [@pike1998reliability], which follows from reliability being a function of the variability in true scores. In modern latent variable modelling, group differences in reliability can also emerge because of failures of measurement invariance across groups (e.g., differences in factor loadings or item difficulty parameters across groups).

Variations in reliability could contribute to the discrepancy between effects in original and replication studies, as well as within replications of the same original effect. After all, it has long been known that measurement error suppresses observed effects and associations [@spearman1904proof]. @stanley2014expectations simulated data of items on a scale based on levels of sampling error and reliability similar to what is standard in psychological research. The results showed that the variation due to measurement error was substantial enough to cause replications of a positive small effect to observe anywhere between a medium negative effect and a large positive effect [@stanley2014expectations]. In summary, studies using unreliable measures are less replicable, even when the measurement is equally reliable between original and replication.

@@

Despite the importance of reliable and valid measurement, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. Specifically, @flake2020measurement identified six key questions that an article should answer to avoid QMPs: the definition of the construct, how and why the measure was selected, how the measure operationalizes the construct, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered clearly based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@@

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also illustrated how QMPs create challenges for replicating researchers. To reconstruct the measurement, replication researchers need to know the items that were used, how they were presented to the subjects, and how to compute the scores. If the measure is not reconstructed exactly, constructs measured by original and replication may differ, possibly creating differences in effect sizes between original and replication studies, resulting in less informative replications.

@@

Our study investigates the relation of reliability and measurement reporting with replicability, using data and reports from the large-scale Many Labs replication projects. First, this study expands on the research by  @stanley2014expectations, to see if reliability is related to replication success in empirical replication data. Specifically, we investigate whether successfully replicated studies differed in reliability from non-replicated studies. @stanley2014expectations assumed reliability to be constant across studies, which we know to be an oversimplification. Therefore, to add further context to the relation between reliability and replication, we also investigate the variation in reliability as observed across labs.

Furthermore, we conceptually replicate the study by @flake2022construct on QMPs in replications and original research in the context of the Many Labs projects. We expand on @flake2022construct by exploring associations between QMPs and the replicability of psychological findings.

@@

Measurement reliability can vary across samples, because the residual variance or the true variance in the item scores, or both, differs between samples. While differences in these variances across samples is inevitable, these differences should not be systematic between replication and original samples for their results to remain comparable. Therefore, we investigated the reliability in replication (Research Question 1a; RQ1a ) and original psychological research (RQ1b). The Many Labs studies were intended as direct replications, which implies that deviations from the original research should be irrelevant for testing the effect [@nosek2022replicability], including systematic differences in reliability (Hypothesis 1; H1).

@@

Additionally, for the results of direct replications to be comparable with each other, the differences in reliability should be comparable. Systematic differences in reliability could indicate that measurement assesses fundamentally different constructs. Therefore, we investigated  whether reliability estimates differed systematically between replicating labs (RQ2). For effect sizes, there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expect that there is no systematic variation in the reliability estimates of replications of the same original study (H2) either.

In theory, there should be a positive relation between reliability and replicability. Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. If the true effect is not null, then the statistical tests with reliable measures are more likely to be significant. To empirically assess this, we investigated the association between replication study reliability and replication outcome (RQ3). We expected that reliability in the replications would be positively associated with replication success (H3).

@@

We conceptually replicate the findings on measurement reporting of @flake2022construct by documenting the frequency of QMPs in replications of psychological research (RQ4a) and original psychological research (RQ4b). @flake2022construct found that RPP replications averaged more QMPs than original studies. We hypothesized that for our Many Labs sample, QMPs would be more frequent in original psychological research than in replication research (H4), because the Many Labs replications used structured protocols documenting the measurement.

QMPs obscure information about a particular measurement, which may cause issues reconstructing that measurement in subsequent replication attempts. Because resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct], we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5). A reduction in QMPs corresponds to greater transparency in measurement reporting. In line with earlier research finding that other transparency-related practices are associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).

@flake2022construct proposed that QMPs in original articles may impede recreating measurements for replications, and indeed @shaw2020measurement found evidence for such a spill-over effect for validity. In line with this research, we investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6). We expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

The data used for the analyses consisted of three main sources: replication datasets, replication protocols, and original study articles. The data came from the Many Labs replication projects. Specifically, data from Many Labs 1, 2, 3, & 5 [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many] was included. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

The unit of analysis in this study was a measure of a single psychological construct used in the primary analysis that was targeted in the replication. Multiple psychological constructs could be measured per original study or replication. We used the replication protocols to identify these measures. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.

@@

We retrieved the data on the replication protocols and replication datasets of Many Labs 1, 2, 3, & 5 from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned to ensure the planned analyses were feasible. However, no coding or analysis of either of them had taken place before we preregistered the analyses. Further details on the search strategy can be found in the [supplementary materials](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) (URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd>).

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study. For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

### Replication Protocols
The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

We identified and retrieved all original study articles using the citations for these articles in each replication protocol.

@@

Because data from the Many Labs replications were available for each lab location within each replication set, we could calculate reliabilities for any item scale measure used for each lab location separately. This allowed us to assess the variation of reliabilities of the same measure across different contexts.

We calculated Cronbach’s Alpha, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], to compare the reliabilities reported in original articles and across replicating labs. We calculated Cronbach’s Alpha using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments. We had preregistered Omega as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd).

@@

We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) of a measure from both the replication protocols and the original articles when present. Similarly, we coded the presence of any validity evidence, such as a factor analysis, that was presented alongside the measure.

The tests for Hypotheses 4, 5, & 6 were all based on the QMPs coded for both original articles and replication protocols. We included items based on Flake et al. (2022), and additional items to further assess transparent measurement reporting as laid out in Flake and Fried (2020). In total, we coded `r sum(colnames(coded_data_replications) == "def1" | colnames(coded_data_replications) == "op_1" | colnames(coded_data_replications) == "op_2" | colnames(coded_data_replications) == "op_3" | colnames(coded_data_replications) == "op_4" | colnames(coded_data_replications) == "op_5" | colnames(coded_data_replications) == "sel_1" | colnames(coded_data_replications) == "sel_2" | colnames(coded_data_replications) == "sel_3" | colnames(coded_data_replications) == "sel_4" | colnames(coded_data_replications) == "quant_1" | colnames(coded_data_replications) == "quant_2" | colnames(coded_data_replications) == "quant_3" | colnames(coded_data_replications) == "quant_4" | colnames(coded_data_replications) == "mod_1" | colnames(coded_data_replications) == "mod_2" | colnames(coded_data_replications) == "mod_3" | colnames(coded_data_replications) == "mod_4" | colnames(coded_data_replications) == "mod_5" | colnames(coded_data_replications) == "mod_6")` different QMPs, categorized into five QMP type categories based on Flake and Fried (2020). The QMP categories and example items can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

QMPs were all coded to be either true, false, or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). For the analyses, we calculated a ratio (both per QMP type and overall QMP) based on the number on the number of true responses divided by the number of responses coded to be applicable.

After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because we considered them overly stringent in practice. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).

@@

We used the published reports of the Many Labs projects [@klein2014investigating; @ebersole2016many; @ebersole2020many; @klein2018many]) to determine replication success based on the reported significance of the meta-analytic effect. An effect was considered successfully replicated if the meta-analytic effect was in the same direction as the original effect and had a p-value lower than .05.

@@

Every hypothesis test in this study was a two-sided test with an alpha of .05. We applied no correction for multiple testing to ensure that the rate of false negatives remained low. Our hypotheses are about associations that have been proposed in the literature, but to the best of our knowledge have not yet been empirically tested on real data. In this exploratory context, we considered false negatives more detrimental than false positives.

@@

Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study, as well as the proportion of successful replications, for each of the Many Labs separately and in total.

@@

### Hypothesis 6: Relation Between QMPs in Original and Replication Research
